Almost compatible functions and infinite length games

### 2016-09-08 articles/almost-compatible-functions-and-topological-games/article.tex
remove contractions

\begin{abstract}
  \(\alcompSP\kappa\) asserts the existence of pairwise
  almost compatible finite-to-one functions \(A\to\omega\) for each
  countable subset \(A\) of \(\kappa\).
  The existence of winning \(2\)-Markov strategies in
  several infinite-length games, including
  the Menger game on the one-point Lindel\"ofication \(\oneptlind\kappa\)
  of \(\kappa\), are guaranteed by \(\alcompSP\kappa\). \(\alcompSP\kappa\) is
  implied by the existence of cofinal Kurepa families of size \(\kappa\),
  and thus holds for all cardinals less than \(\aleph_\omega\).
  It's consistent that \(\alcompSP{\aleph_\omega}\) fails, but
  there must always be a winning \(2\)-Markov strategy for the second
  player in the Menger game on \(\oneptlind{\omega_\omega}\).
\end{abstract}

@@

  In \cite{MR1129143}, Scheepers noted that \(\alcompS{\omega_1}\) holds in \(ZFC\),
  and that it's possible to force \(\mf c\) to be arbitrarily large
  while preserving \(\alcompS{\mf c}\). However, \(\alcompS{\mf c^+}\) always fails.
  This axiom may be applied to obtain a winning \(2\)-tactic for \(\pl F\)
  in the countable-finite game.

@@

  This characterization is slightly different than the typical characterization
  in which the second player first chooses a specific
  finite subcollection \(\mc F_n\) of the cover itself and lets
  \(F_n=\bigcup \mc F_n\), denoted as \(G_{fin}(\mc O,\mc O)\)
  in \cite{MR1378387}.
  However, it's easily seen that these games are equivalent
  for perfect information strategies (so both characterize
  the Menger property in the same way), and this characterization is
  more convenient for our concerns.

@@

  The relationship between \(\schFillStrictGame\kappa\) and
  \(\menGame{\oneptlind\kappa}\) is strong; in both games \(\pl C\) essentially
  chooses a countable subset of \(\kappa\) followed by \(\pl F\) choosing
  a finite subset of that choice, and it's easy to see the winning perfect
  information strategy for \(\pl F\) in both games.
  In addition, it was shown in
  \cite{clontzMengerGamePreprint} that when \(\alcompS{\kappa}\) holds,
  \(\pl F\) has a winning \(2\)-Markov strategy in
  \(\menGame{\oneptlind\kappa}\).

@@

  Although, it's still open whether the previous two questions are even
  distinct.

>>>>

\begin{abstract}
  \(\alcompSP\kappa\) asserts the existence of pairwise
  almost compatible finite-to-one functions \(A\to\omega\) for each
  countable subset \(A\) of \(\kappa\).
  The existence of winning \(2\)-Markov strategies in
  several infinite-length games, including
  the Menger game on the one-point Lindel\"ofication \(\oneptlind\kappa\)
  of \(\kappa\), are guaranteed by \(\alcompSP\kappa\). \(\alcompSP\kappa\) is
  implied by the existence of cofinal Kurepa families of size \(\kappa\),
  and thus holds for all cardinals less than \(\aleph_\omega\).
  It is consistent that \(\alcompSP{\aleph_\omega}\) fails, but
  there must always be a winning \(2\)-Markov strategy for the second
  player in the Menger game on \(\oneptlind{\omega_\omega}\).
\end{abstract}

@@

  In \cite{MR1129143}, Scheepers noted that \(\alcompS{\omega_1}\) holds in \(ZFC\),
  and that it is possible to force \(\mf c\) to be arbitrarily large
  while preserving \(\alcompS{\mf c}\). However, \(\alcompS{\mf c^+}\) always fails.
  This axiom may be applied to obtain a winning \(2\)-tactic for \(\pl F\)
  in the countable-finite game.

@@

  This characterization is slightly different than the typical characterization
  in which the second player first chooses a specific
  finite subcollection \(\mc F_n\) of the cover itself and lets
  \(F_n=\bigcup \mc F_n\), denoted as \(G_{fin}(\mc O,\mc O)\)
  in \cite{MR1378387}.
  However, it is easily seen that these games are equivalent
  for perfect information strategies (so both characterize
  the Menger property in the same way), and this characterization is
  more convenient for our concerns.

@@

  The relationship between \(\schFillStrictGame\kappa\) and
  \(\menGame{\oneptlind\kappa}\) is strong; in both games \(\pl C\) essentially
  chooses a countable subset of \(\kappa\) followed by \(\pl F\) choosing
  a finite subset of that choice, and it is easy to see the winning perfect
  information strategy for \(\pl F\) in both games.
  In addition, it was shown in
  \cite{clontzMengerGamePreprint} that when \(\alcompS{\kappa}\) holds,
  \(\pl F\) has a winning \(2\)-Markov strategy in
  \(\menGame{\oneptlind\kappa}\).

@@

  Although, it is still open whether the previous two questions are even
  distinct.
